### 2022-05-27 Publish Paper/manuscript_main.tex
Update Published Paper
+ VN abstract
+ Eng paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. \cite{01284} also used Deep Convolution Neural Network. However, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative
Learning Strategy which can more effectively balance representation learning and
classifier learning without additional computational cost. Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretability methods that can highlight pixels that the trained network deems
relevant for the final classification.\\

@@

The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, I found out that the age category miss 57 data point, then I decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these unknowns data point is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.

@@

In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, I will analyze the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models wich have been used as a backbone model in this paper will be discuss more in the Related Work section. \\
In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. \cite{01284} also used Deep Convolution Neural Network. Moreover, that paper used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost. Another state of the art is GradCam and Kernel SHAP\cite{06612}, which are both model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\

@@

The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, the age category miss 57 data point, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these unknowns data point is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.

@@

In this paper, the backbone models that have been used are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  

### 2022-05-27 Publish Paper/manuscript_title_etc.tex
Update Published Paper
+ VN abstract
+ Eng paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Nowadays, the dramatic development of the big city and industrial zones leads to a higher rate of skin disease because of polluted air. Moreover, in many developing countries, the hospital is being overloaded every single day by the huge number of the patient. They need a fast and accurate solution to diagnose skin disease before meeting the doctor or how to create an optimized and balanced model for skin lesion classification. After the literature review process, I found that there are many outstanding papers on both Deep Learning and Machine Learning. In Deep Learning, they often use transfer learning. Some new approaches are GradCam, Kernel Shap, Student and Teacher model. In Machine Learning, Random Forest, and Support Vector Machine are applied. The main focus of this research is to analyze the effect of metadata on the combination of the backbone model and the Soft-Attention layer. The soft-Attention layer is tested in a previous paper that improve the model performance to 92 percent accuracy. I also try some other combinations to construct an optimized model that can use on mobile phone. After the experiment process, I found out that metadata and weighted loss function makes the performance of the model less imbalanced with 90 percent accuracy but its f1-score and recall score standard deviation is 0.08 and 0.09, respectively. I also construct a model with the combination of MobileNetV3Large and Soft-Attention layer with image and metadata input with 86 percent accuracy but thirty times as fast as the highest performance model.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
Today, the rapid development of big cities and industrial zones leads to an increasing incidence of skin diseases because of air pollution. According to a survey by the American Cancer Society, there are about 100,000 people with skin cancer and more than 7,600 people are predicted to not survive by 2022. Therefore, a tool to support the diagnosis of skin cancer quickly and accurately is needed in the context of hospitals being overwhelmed every day by the large number of patients in many developing countries. In the past half-decade, technologies belonging to the 4.0 technology group are rapidly changing our lives, including Artificial Intelligence, Machine Learning and Deep Learning. Deep Learning and Machine Learning have also been applied to build diagnostic models of skin pathologies. Some of the new approaches are GradCam, Kernel Shap and the Student-Teacher model. In Machine Learning, Random Forest and Support Vector Machine are applied. The data used in this study is HAM10000 which is an imbalanced dataset. Several methods have been applied including data augmentation, Soft-Attention, and balanced resampling. In this study, the models DenseNet201, InceptionResNetV2, ResNet50, ResNet152, NasNetLarge are combined with Soft Attetion by replacing the last 2 CNN blocks with Soft-Attetnion. Moreover, metadata is used as a sub input layer in the model. Besides, weight loss function is applied, the way of calculating weight will be shown in this paper. Soft Attention was tested in an earlier paper to improve the model's performance with 92 percent accuracy. In addition, MobileNetV2, MobileNetV3 and NasNetMobile models are also studied to deploy solutions on phones. After testing, the performance of DenseNet201 model combined with Soft-Attetion using baseline data and weighted loss function reached 90 percent accuracy but standard deviation of f1 score and recall score of it is 0.08 and 0.09, respectively, compared to the standard deviation of the f1 index and the recall index of 0.22 and 0.27 of the previous paper, respectively.A model with combination of MobileNetV3Large and Soft-Attention layer with baseline data and image input have been constructed that achieve 86 percent accuracy but training time takes 116 seconds per training session.
}
